---
title: "R Notebook"
output: html_notebook
---


```{r}
library(readr)
neighbourhood_rating <- read_csv("data/neighbourhood_rating.csv") %>% clean_names()
View(neighbourhood_rating)
```

```{r}
green_spaces %>% 
  glimpse()

```

```{r}
community_belonging %>% 
  glimpse()

```

```{r}
neighbourhood_rating %>% 

  glimpse()

```





#1  iwill try to compine all dataset together
# gerrn speace
```{r}
green_f_code <-
green_spaces %>% 
  distinct(feature_code)
green_f_code
green_spaces %>% 
  distinct(units)
```

#neighbourhood
```{r}
neighbourhood_feat <- neighbourhood_rating %>% 
distinct(feature_code)

neighbourhood_feat

```

```{r}
neighbourhood_rating %>% 
  distinct(units)
```
# the same to the community dateset

```{r}
community_feach <- community_belonging %>% 
  distinct(feature_code)
community_belonging %>% 
  distinct(units)
```


```{r}
community_feach 
neighbourhood_feat
green_f_code
```
#the 3 dateset has the same varble number 
#try to see if the ary equal 

```{r}
all_equal(green_f_code, neighbourhood_feat, community_feach )
```
```{r}
full_join(green_f_code, neighbourhood_feat, community_feach,"feature_code" )
```
#join tow date set together

```{r}
green_neighbour <-
full_join(green_spaces, neighbourhood_feat,"feature_code")
```

```{r}
green_neighbour
```
#add new feachwe code colmun  (authority S92000003 = Sctland)
```{r}
green_neighbour<-
green_neighbour %>% 
  mutate(authority  = "S92000003")
green_neighbour 
```

```{r}
green_neighbour <-
 green_neighbour %>% 
  arrange(feature_code)
```



#join the date set together 
```{r}
neighb<-
  full_join(neighbourhood_rating, green_neighbourhood, "feature_code")
```
#add new colmn year to look at the date in deifrnt years 
```{r}
neighbourhood_rating<-
neighbourhood_rating %>% 
  mutate(year  = "2019")
neighbourhood_rating
```

```{r}
all_equal(neighbourhood_rating,green_neighbour)
```

```{r}
neighbourhood_rating<-
neighbourhood_rating %>% 
  mutate(year  = "2019")
neighbourhood_rating
```

```{r}
all_equal(neighbourhood_rating,green_neighbourhood)
```




```{r}
neighb<-
  full_join(neighbourhood_rating, green_neighbour, "feature_code")
```

```{r}
com <-
  full_join(community_belonging, green_neighbourhood, "feature_code")
```

```{r}
all_equal(,neighbourhood_rating)
```

```{r}
community_belo<-
community_belonging %>% 
  mutate(year  = "2019")
neighbourhood_rating
```

#community
#the date cant joinging  to  mne becuse of they are not the same dim
```{r}
ommun <-
full_join(community_belonging, green_neighbour, "authority ")

```
```{r}
community_belonging <-
community_belonging %>% 
mutate(authority  = "S92000003")
community_belonging
```
```{r}
ommun <-
full_join(community_belonging, green_neighbour, "feature_code")

```
#is they any missing value?
```{r}
green_neighbour%>% 
summarise(across(.fns = ~sum(is.na(.x))))

```

```{r}
green_spaces%>% 
summarise(across(.fns = ~sum(is.na(.x))))

```
#i did not found any NA

# filter coulmn measurement to use it in the feutcuer 
```{r}
green <-
green_neighbour%>%
  filter(measurement == "Percent") %>% 
  select(-c(units, measurement))
```

```{r}
community <-
community_belonging%>%
  filter(measurement == "Percent") %>% 
  select(-c(units, measurement))
```

```{r}
neighbour <-
neighbourhood_rating %>%
  filter(measurement == "Percent") %>% 
  select(-c(units, measurement))
```

# povit wider to see the value 
```{r}
green %>% 
  pivot_wider(names_from = distance_to_nearest_green_or_blue_space,
              values_from = value)
```


```{r}
neighbour %>% 
  distinct(household_type) 
```

```{r}
neighbour %>% 
  distinct(walking_distance_to_nearest_greenspace)
```

```{r}
green_clean <-
green %>% 
  pivot_wider(names_from = distance_to_nearest_green_or_blue_space,
              values_from = value) %>% 
  clean_names()
```

#tack year 2019  as group
```{r}
green_2019 <-
green %>%
  filter(feature_code== "S92000003",
         date_code == 2019)

```

```{r}
green_2019 <-
green_clean %>%
  filter(feature_code== "S92000003",
         date_code == 2019)
```

```{r}
green_2019
```

```{r}

  ggplot(green_2019) +
  geom_col(aes(x = distance_to_nearest_green_or_blue_space,y=  , fill = urban_rural_classification), position =  "dodge")
  
```

```{r}
green_all <-
green_2019 %>% 
  filter(age == "All", 
         gender == "All",
         urban_rural_classification == "All",
         simd_quintiles == "All",
         type_of_tenure == "All",
         household_type == "All",
         ethnicity == "All") %>% 
  arrange(authority, date_code)
green_all
```

```{r}
ggplot(green_all) +
  geom_col(aes(x = date_code,y= value , fill = distance_to_nearest_green_or_blue_space), position =  "dodge")
```
```{r}
ggplot(green_2019) +
  aes(x =urban_rural_classification, y =distance_to_nearest_green_or_blue_space, fill = value) +
  geom_col(position = "dodge") 
 
```
```{r}
ggplot(green_all) +
  aes(x = date_code, y =value, fill = urban_rural_classification) +
  geom_col(position = "dodge") +
  coord_flip()
```


```{r}
```

```{r}
green_spaces %>% 
    filter(age == "All", 
         gender == "All",
         urban_rural_classification == "All",
         simd_quintiles == "All",
         type_of_tenure == "All",
         household_type == "All",
         ethnicity == "All",
         measurement == "Percent") %>% 
arrange(feature_code, date_code)


```



#filter it by scotland code 

```{r}
green_2018 <-
green %>%
  filter(feature_code== "S92000003",
         date_code == 2018)
```

```{r}
green_all_2018 <-
green_2018 %>% 
  filter(age == "All", 
         gender == "All",
         urban_rural_classification == "All",
         simd_quintiles == "All",
         type_of_tenure == "All",
         household_type == "All",
         ethnicity == "All") %>% 
  arrange(authority, date_code)

ggplot(green_all_2018) +
  geom_col(aes(x = date_code,y= value , fill = distance_to_nearest_green_or_blue_space), position =  "dodge")
green_all_2018
```

```{r}
green_all_2018
```

